A Digital Library for Crowds on the Real-Time Social Web

### 2011-05-05 docs/csce_675/paper.tex
Minor modifications to paper.

\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework. It can appear both before and after the grouper module depending upon its funcationality. In the figure we have showed the module appear before grouper only. When the module appears before the grouper, it is used to weed out information unnecessary for the grouper. For example in case of crowd detection, it remove information like spam messages. When the module appears after the grouper, it cleans the data generated by the grouper. For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees. 
The module can also have additional function like search.

% \begin{itemize}
%   \item \noindent\textbf{Crawler}: This module deals with interacting with social media websites to collect information. For this project we will be collecting data from Twitter using Twitter Streaming APIs.
%   \item \noindent\textbf{Filter}: This module removes unwanted data like spam messages, from data collected by the crawler.
%   \item \noindent\textbf{Grouper}: The grouper module analyses the data collected, to determine crowds and adds them to the DBMS. 
%   \item \noindent\textbf{HTTP JSON RESTful APIs}: This module will expose a HTTP-based API that clients can query to get data from the collection. The API will return crowds, users, and their tweets.
% \end{itemize}

% \begin{itemize}
%   \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
%    \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
%    \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
% \end{itemize}

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}
The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

@@

>>>>

\section{Crowd Discovery Algorithm}
\label{sec:crowd_algorithm}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{images/intro}
\caption{Example of crowd discovery and tracking in Twitter.}
\label{fig:intro-example}
\end{figure}
To illustrate the problem of crowd discovery, consider the simple example in
Figure~\ref{fig:intro-example}. At time t=1, users A and B send messages to each
other, as do users C and D.\footnote{For simplicity, the example discretizes
time so that all messages between users occur in steps. In practice, the proposed
algorithm relaxes this assumption and can handle arbitrary message sending
times.} The associated communication graph shows an edge between the two pairs,
where for simplicity the edge is annotated with the number of messages between
the users (2, in both cases). Further, suppose we identify crowds based purely on
graph connectivity. So for time t=1, we see there are two crowds discovered
\{A,B\} and \{C,D\}. For each crowd, we can characterize the semantics of their
communication with simple keywords extracted from the content of the tweets:
(``oil'', ``gulf'') and (``walcott'', ``capello''). At time t=2, the
communication graph is updated with a new edge (connecting User A and User C),
and the existing edges are decayed by one (again, a simplifying assumption for
the purposes of this example). A single crowd is discovered since all users are
connected via edges with non-zero edge weights. At time t=3, User D leaves the
main crowd since no messages to or from User D have been observed since time t=1.
This process continues until time t=5 when User C also leaves the main crowd due
to inactivity. Note that crowds are discovered from communication graph only and
not from the content of the messages. As an example of crowd tracking, we can
track the evolution of the yellow crowd across time periods, observing the
changes it goes through as it grows in size from t=1 to t=2 and then reduces to
two users by t=5.

The grouper deals with the transient crowd discovery and tracking in systems like Facebook and Twitter. For practical crowd discovery and tracking in a large time-evolving communication network, however, we face four key challenges:

@@

\medskip \noindent \textbf{Filter}: This module is used to filter un-necessary data from the framework. It can appear both before and after the grouper module depending upon its funcationality. In the figure we have showed the module appear before grouper only. When the module appears before the grouper, it is used to weed out information unnecessary for the grouper. For example in case of crowd detection, it remove information like spam messages. When the module appears after the grouper, it cleans the data generated by the grouper. For, example in case of crowd detection, it analyzes crowds discovered by the grouper and removes un-necessary crowds, or crowds that don't meet specific quality guarentees. The module can also have additional functions that support features like search.

\medskip \noindent \textbf{HTTP JSON RESTful APIs}: This module provides client an interface to the digital library. The module exposes JSON APIs that the clients can use to browze and search the crowds archive.

\begin{itemize}
  \item \noindent\textbf{Beanstalk}: Beanstalk is a simple, fast work queue. We use it to connect the crawlers, filters, and groupers together.
   \item \noindent\textbf{Tornado}: Tornado is an open source, non-blocking web server.  We choose it because it is fast and scalable.
   \item \noindent\textbf{MongoDB}: MongoDB is a scalable, high-performance, open source, document-oriented database. We store the crowds discovered by the framework in this DB. The API module interacts with this database to retrieve collections as required by the user query.
\end{itemize}
